Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-29 manuscript/manuscript.Rmd
mini

This time series is representative of the patterns observed in the data (see App. A).
The episode reward and episode length statistics are shown in Fig. \ref{fig:rew_len_fig}.
There, we highlight two things:
First, that the tendency towards early episode ends is fixed by the conservative approach of fishing at 80% of the MSY mortality rate.
(In App. B we discuss and evaluate other policies using a fixed-percentage of the MSY mortality rate.)
Second, that while the conservative 80% approach has a stable behavior, it consistently produces smaller harvests than a DRL generated policy.

@@

Notice the anti-correlation between $X$ and $Y$ along the paths, this is especially prominent for the constant mortality plots.
This anti-correlation is, furthermore, observed in the time series plots (see Fig. \ref{fig:timeseries} and App. A).

>>>>

This time series is representative of the patterns observed in the data (see App. A.1).
The episode reward and episode length statistics are shown in Fig. \ref{fig:rew_len_fig}.
There, we highlight two things:
First, that the tendency towards early episode ends is fixed by the conservative approach of fishing at 80% of the MSY mortality rate.
(In App. A.2 we discuss and evaluate other policies using a fixed-percentage of the MSY mortality rate.)
Second, that while the conservative 80% approach has a stable behavior, it consistently produces smaller harvests than a DRL generated policy.

@@

Notice the anti-correlation between $X$ and $Y$ along the paths, this is especially prominent for the constant mortality plots.
This anti-correlation is, furthermore, observed in the time series plots (see Fig. \ref{fig:timeseries} and App. A.1).
